Output Summary

### 2023-07-15 03-post-process/ms-content/ms-content.Rmd
Enable toggling on/off ms-content analyses one at a time

---
output: 
  pdf_document:
    keep_tex: true
params:
  scenario:
    label: "Scenario"
    value: "base_vlong"
    input: text
  thin_percent:
    label: "Proportion of Posterior Samples to Retain?"
    value: 1
    input: numeric
  include_sim_years:
    label: "Include Simulated Years on Plots?"
    value: FALSE
header-includes:
  - \usepackage{sansmathfonts}
  - \usepackage{helvet}
  - \renewcommand{\rmdefault}{\sfdefault}
  - \usepackage{float}
  - \usepackage[labelfont={bf,sc},labelsep=period]{caption}
  - \captionsetup{width=\textwidth}
editor_options: 
  chunk_output_type: console
---

@@

@@

```{r beta-fig, fig.width = 3.4, fig.height = 3.4, fig.cap = msdown::prep_caption(beta_caption), time_it = TRUE}
# extract posterior summaries of the capacity parameters
beta_ests = post_summ(post, "^beta[", probs = c(0.025, 0.1, 0.5, 0.9, 0.975))

@@

```{r relationship-fig, fig.width = 7.2, fig.height = 9, fig.cap = msdown::prep_caption(relationship_caption), time_it = TRUE}
solid_col = "grey30"
tranp_col = alpha(solid_col, 0.25)
pt_cex = 1.3

@@

```{r no-fall-fig, fig.width = 3.4, fig.height = 3.4, fig.cap = msdown::prep_caption(no_fall_caption), time_it = TRUE}
cv = function(x) {sd(x, na.rm = TRUE)/mean(x, na.rm = TRUE)}

>>>>

---
output: 
  pdf_document:
    keep_tex: true
params:
  scenario:
    label: "Scenario"
    value: "base_vlong"
    input: text
  thin_percent:
    label: "Proportion of Posterior Samples to Retain?"
    value: 1
    input: numeric
  beta_fig:
    value: TRUE
  relationship_fig:
    value: TRUE
  no_fall_fig:
    value: TRUE
header-includes:
  - \usepackage{sansmathfonts}
  - \usepackage{helvet}
  - \renewcommand{\rmdefault}{\sfdefault}
  - \usepackage{float}
  - \usepackage[labelfont={bf,sc},labelsep=period]{caption}
  - \captionsetup{width=\textwidth}
editor_options: 
  chunk_output_type: console
---

@@

::: {.normalsize data-latex=""}
**Scenario:** ``r params$scenario``  
**Kept MCMC Iterations:** `r paste0(params$thin_percent * 100, "\\%")`
:::

@@

```{r beta-fig, fig.width = 3.4, fig.height = 3.4, fig.cap = msdown::prep_caption(beta_caption), time_it = TRUE, eval = params$beta_fig}
# extract posterior summaries of the capacity parameters
beta_ests = post_summ(post, "^beta[", probs = c(0.025, 0.1, 0.5, 0.9, 0.975))

@@

```{r relationship-fig, fig.width = 7.2, fig.height = 9, fig.cap = msdown::prep_caption(relationship_caption), time_it = TRUE, eval = params$relationship_fig}
solid_col = "grey30"
tranp_col = alpha(solid_col, 0.25)
pt_cex = 1.3

@@

```{r no-fall-fig, fig.width = 3.4, fig.height = 3.4, fig.cap = msdown::prep_caption(no_fall_caption), time_it = TRUE, eval = params$no_fall_fig}
cv = function(x) {sd(x, na.rm = TRUE)/mean(x, na.rm = TRUE)}
